Effects of the 2014 Russian Annexation of Crimea on Russian Seafood Trade

### 2022-08-11 Russia Case Study under the hood.Rmd
Case Study Final Draft is the RMD for the finished writeup. Russia Case Study under the hood includes the complete writeup, plus code for unused charts, tables, and vectors to find unused data, like species of each exporting country

Russia began an annexation on Ukraine’s Crimean peninsula on March 18, 2014, sparking international tensions that imposed sanctions on Russia (Biersak, 2014). Sanctions included freezing Russian assets and capturing property to restrict Russian access to Western markets, aiming to cripple their banking, energy, and defense sectors; and banning exports to Russia of military technology and dual-use goods, including oil exploration and production equipment. (DeYoung; Christie). In response, Russia provided counter-sanctions as an agricultural embargo in 2014 that banned itself from importing food items, including seafood, from sanctioning nations (Wegren, 2018). With market data available from before and after the 2014 Annexation, this case study seeks to understand the seafood trade flow amid various embargoes and sanctions to better understand whose exports to Russia increased and whose decreased, and how much of that trade entered the market through third-party exporters to complete trades to and from Russia. Data from this case study can help predict market shifts and patterns to the current Ukrainian-Russian war that has seen similar sanctions and alliances rise up again.

@@

@@

```{r, echo=FALSE}
  kable(tmp, caption = "Top 10 Importers of Russian Goods")
```

Germany, The United States, and South Korea all decreased their imports from Russia after the annexation, although only Germany and the United States had imposed sanctions on Russia and faced the agricultural embargo. Kazakhstan took the place of the USA in the top 10 importers after the annexation, but it was not enough to make up the difference from losses by the USA.

@@

Due to Russia's agricultural embargo counter-sanction, Russia ramped up domestic good production, primarily in capture fisheries. In most cases, importing countries bought more capture products than aquaculture, with the exceptions being Great Britain, Moldova, Azerbaijan, and Vietnam. Great Britain stopped importing goods from Russia after 2014, and neither Moldova, Azerbaijan, nor Vietman imported capture seafood in either time period. Azerbaijan and Vietnam did not import any aquaculture products prior to 2014, but did after.

@@

```{r, echo=FALSE}
top_importers_all_years %>%
  select(-c(`Aquaculture Live Weight 2010-2014 (Tons)`:`Capture Live Weight 2015-2019 (Tons)`))%>%
  slice(-c(11:15)) %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(sanctions_towards_russia = case_when(
      Importer %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
  ggplot(aes(x = Importer, y = `Percent Change`)) +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Importer, yend = Importer, color = sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Importer, color = sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Importers")+
  ggtitle("Percent Change in Imports from Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Imposed Sanctions Against Russia"))+
      geom_vline(xintercept = 0)

@@

Some importing nations had more drastic changes in imports before and after the Annexation than others. The USA and Germany, for example, saw over a 50% decrease in imports from Russia, while other countries like the Netherlands and Nigeria experienced a 50% increase in Russian imports.

@@

```{r, echo=FALSE}
kable(top_exporters_all_years, caption = "Top 10 Exporters to Russia")
```

Top seafood exporters to Russia include China, Iceland, Latvia, Morocco, Norway, and Ukraine, which all decreased total exports in the five years following the 2014 Annexation. Latvia, Iceland, Norway, and Ukraine stopped exporting to Russia completely due to the embargo. In their place, Greenland, India, Mauritania, and Thailand rose to the top 10 exporters to Russia. These replacements also did not make up the difference from the lost tonnage of Iceland, Latvia, Norway, and Ukraine.

```{r, echo=FALSE, message=FALSE}

@@

```{r, echo=FALSE, fig.width=6}
full_join(artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014, importer_iso3c == "RUS") %>%
   group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
   summarise(`Live weight 2010-2014` = sum(live_weight_t)),
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
    group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
    summarise(`Live weight 2015-2019` = sum(live_weight_t)), by = "exporter_iso3c") %>%
  pivot_longer(names_to = "time_period", values_to = "live_weight", 
               cols = c(`Live weight 2010-2014`,`Live weight 2015-2019`)) %>%
  arrange(desc(live_weight)) %>%
    filter(exporter_iso3c == "NOR" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR" | 
          exporter_iso3c == "MRT" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "IND" |
          exporter_iso3c == "GRL" |
          exporter_iso3c == "THA" ) %>%
  ggplot(aes(x= time_period, y = live_weight, color = exporter_iso3c, group = exporter_iso3c))+
  geom_line() +
  geom_point() +
 # scale_color_brewer(palette = "Paired")+
  xlab("")+
  ylab("Live Weight (Tons)")+ 
  ggtitle("Total Exports Before and After Annexation", subtitle = "Countries Exporting Seafood to Russia Faceted by Russian Embargo Counter-Sanction") +
 guides(col = guide_legend(title = "Russian Seafood Exporters"))+
   scale_y_continuous(breaks = seq(0, 2000000, by = 2000000))+
  scale_y_continuous(labels = scales::comma)+  
#  geom_segment(x = as.numeric(time_period), xend = as.numeric(time_period), y = 0, yend = 1000000)+
  facet_wrap(~exporter_sanctions_towards_russia.x)+
    theme(axis.text.x = element_text(angle = 10))

@@

Despite the initial dip in exports after the annexation, many countries' exports still increased overall between the two time periods. China and Morocco, in the countries who did not impose sanctions, saw their total exports fall, as did each country affected by the embargo, except for Denmark.
```{r, echo=FALSE}
top_exporters_all_years %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      Exporter %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "yes",
      TRUE ~ "no"
    )) %>%
  ggplot() +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Exporter, yend = Exporter, color = exporter_sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Exporter, color = exporter_sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Exporters")+
  ggtitle("Percent Change in Exports to Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Sanctions Imposed by Russia"))+
      geom_vline(xintercept = 0)
```

@@

Trade trends with Russia can be seen when the imports and exports are broken down by the top species, rather than country. Russia stopped importing as many seafood goods due to its agricultural embargo, and instead increased domestic supply to become more agriculturally self-reliant and food secure (Wegner, 2018). It exported much more than it did prior to the Annexation, and exported more than it imported by an order of magnitude. Russia’s primary method was wild capture fisheries.

@@

ggplot(artis_russia_2009_2019 %>%
         filter(year %in% 2010:2019) %>%
  filter( importer_iso3c == "RUS") %>%
 filter(sci_name == "clupea harengus" | sci_name == "osteichthyes" | sci_name == "salmo salar" | sci_name == "animalia" | sci_name == "scomber scombrus" | sci_name == "sardina pilchardus" | sci_name == "sprattus sprattus" | sci_name == "mallotus villosus" | sci_name == "actinopteri" | sci_name == "oncorhynchus mykiss" | sci_name == "pangasianodon hypophthalmus"| sci_name == "mytilus chilensis"))+
    geom_col(aes(x= year, y= live_weight_t, fill = sci_name))+
              facet_wrap(~method)+
  scale_color_solarized()+
  ggtitle("Top Russian Seafood Imports")+
  xlab("Year")+
  ylab("Live Weight (Tons)")+
  guides(fill = guide_legend(title = "Species"))+
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks = seq(0,800000,by = 100000))+
  scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)

@@

```{r, include=FALSE}
# Animalia does not show up color-wise as great here because it spans multiple 4digit codes, whereas the ones above were grouped by sci name, not hs 4 digit code

@@

```{r, fig.height=6, fig.width=7, include=FALSE}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r, fig.cap="Filtered by Change greater than 10", fig.height=6, message=FALSE, include=FALSE}
russian_import_change %>%
  rename(`Russian Import Trade Change` = russian_import_change_weight, `Russia-exempt Import Trade Change` = total_trade_change) %>%
  filter(exporter_iso3c != "RUS") %>%
  filter(abs(`Russian Import Trade Change`) > 10000 |
           abs(`Russia-exempt Import Trade Change`) > 10000) %>%
  select(exporter_iso3c, `Russian Import Trade Change`, `Russia-exempt Import Trade Change`, exporter_sanctions_towards_russia) %>%
  pivot_longer(`Russian Import Trade Change`:`Russia-exempt Import Trade Change`, names_to = "trade_type", values_to = "trade_change") %>%
  ggplot()+
  geom_segment(mapping = aes( x = 0, xend = trade_change, y = exporter_iso3c, yend = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
  geom_point(mapping = aes(x= trade_change, y = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
    geom_vline(xintercept = 0) +
    theme_bw()+
  xlab("Live Weight (Tons)")+
  ylab("Exporters to Russia")+
  ggtitle("Russian Imports Trade Change after Annexation", subtitle = "Faceted by Embargoed Nations")+
  scale_x_continuous(breaks= seq(-2500000, 3000000, by = 1000000))+
  scale_x_continuous(labels= scales::comma) +
  facet_wrap(~exporter_sanctions_towards_russia)+
      guides(col = guide_legend(title = "Trade Type"))

@@

There was little trade change in countries who did not face the embargo, but in countries that did, their total trade decreased, except for, again, Denmark. Russia did not import as many goods from China, even though it's exports to China increased. This was a common theme in Russian trade after the Annexation. In nations that faced the embargo, their total exports decreased as well.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

@@

Countries that imposed sanctions on Russia, for the most part, still continued or increased their Russian seafood imports. The exceptions were Germany, and the USA. South Korea's imports also decreased, but it wouldn't adopt Western sanctions against Russia until the Russian-Ukrainian War in 2022. Still, with variable degrees of import changes indeterminate of sanction status, there is no clear trend to predict import changes.

@@

The species did not change, either. The species trade was broken down to see if certain embargoed products were being reworked into a non-agricultural good, but the top HS codes did not change, and included HS 03, 05, 16, and 23, corresponding to fresh, chilled, or frozen fish and invertebrates; animal products; prepared seafood; and fish meal, respectively. No change in HS code trade shows that there was no tertiary market for alternate seafood goods trying to bypass the embargo.

This is shown, too, in total trade changes between Russia and the global seafood trade network. Most nations that enacted sanctions towards Russia saw an increase in imports directly from Russia and an increase in total imports originating in Russia. Their total exports, however, decreased, when they were banned from exporting to Russia. This may be a constraint of the data set, however, as every piece of data was connected to Russia in some way. The opposite happened in Denmark, which experienced an increase in both Russia and total trade. Future work may include expanding trade view around Denmark to include nations using Danish waters and docking in Denmark, or if embargoed nations traded more with Denmark.

The total trade decreases and unchanging HS codes show that there likely was no tertiary market that embargoed nations were using to get their seafood products to Russia. Overall, they were buying more goods, but selling less.

>>>>

Russia began an annexation on Crimea in Ukraine on March 18, 2014, sparking international tensions and sanctions enacted against Russia (Biersak, 2014). Sanctions included freezing Russian assets and capturing property to restrict Russian access to Western markets, aiming to cripple their banking, energy, and defense sectors; and banning exports to Russia of military technology and dual-use goods, including oil exploration and production equipment. (DeYoung; Christie). In response, Russia provided counter-sanctions, most notably as an agricultural import ban set in August 2014 that banned itself from importing food items, including seafood, from sanctioning nations (Wegren, 2018). With market data available from before and after the 2014 Annexation, this case study seeks to understand the seafood trade flow amid various embargoes and sanctions to better understand whose exports to Russia increased and whose decreased, and how much of that trade entered the market through third-party exporters to complete trades to and from Russia. Data from this case study can help predict market shifts and patterns to the current Ukrainian-Russian war that has seen similar sanctions and alliances rise up again.

@@

![ISO 3 Codes](https://www.researchgate.net/profile/Chahir-Zaki/publication/23779008/figure/tbl7/AS:669253044801551@1536573768865/List-of-countries-by-code-iso-3.png)

@@

```{r}
  kable(tmp, caption = "Top 10 Importers of Russian Goods")
```

Germany, The United States, and South Korea all decreased their imports from Russia after the annexation, although only Germany and the United States had imposed sanctions on Russia and faced the agricultural embargo. Kazakstan took the place of the USA in the top 10 importers after the annexation, but it was not enough to make up the difference from losses by the U.S.A.

@@

Due to Russia's agricultural embargo counter-sanction, which banned itself from importing agricultural goods from countries who imposed sanctions against Russia, Russia ramped up domestic good production, primarily in capture fisheries. In most cases, importing countries bought more capture products than aquaculture, with the exceptions being Great Britain, Moldova, Azerbaijan, and Vietnam. Great Britain stopped importing goods from Russia after 2014, and neither Moldova, Azerbaijan, nor Vietman imported capture seafood in either time period. Azerbaijan and Vietnam did not import any aquaculture products prior to 2014, but did after.

@@

```{r}
top_importers_all_years %>%
  select(-c(`Aquaculture Live Weight 2010-2014 (Tons)`:`Capture Live Weight 2015-2019 (Tons)`))%>%
  slice(-c(11:15)) %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(sanctions_towards_russia = case_when(
      Importer %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "Yes",
      TRUE ~ "No"
    )) %>%
  ggplot(aes(x = Importer, y = `Percent Change`)) +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Importer, yend = Importer, color = sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Importer, color = sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Importers")+
  ggtitle("Percent Change in Imports from Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Imposed Sanctions Against Russia"))+
      geom_vline(xintercept = 0)

@@

Some importing nations had more drastic changes in imports before and after the Annexation thatn other. The USA and Germany, for example, saw over a 50% decrease in imports from Russia, while other countries like the Netherlands and Nigeria experienced a 50% increase in Russian imports.

@@

```{r}
kable(top_exporters_all_years, caption = "Top 10 Exporters to Russia")
```

Top seafood exporters to Russia include China, Iceland, Latvia, Morocco, Norway, and Ukraine, which all decreased total exports in the five years following the 2014 Annexation. Latvia, Iceland, Norway, and Ukraine stopped exporting to Russia completely. These four countries enacted sanctions against Russia in response to the Annexation, which meant that the Russian food embargo was placed on them in turn. In their place, Greenland, India, Mauritania, and Thailand rose to the top 10 exporters to Russia. These replacements also did not make up the difference from the lost tonnage of Iceland, Latvia, Norway, and Ukraine.

```{r, echo=FALSE, fig.cap= "Faceted by countries who imposed sanctions on Russia", message=FALSE}

@@

```{r, fig.width= 8}
full_join(artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014, importer_iso3c == "RUS") %>%
   group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
   summarise(`Live weight 2010-2014` = sum(live_weight_t)),
  artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019, importer_iso3c == "RUS") %>%
    group_by(exporter_iso3c, exporter_sanctions_towards_russia) %>%
    summarise(`Live weight 2015-2019` = sum(live_weight_t)), by = "exporter_iso3c") %>%
  pivot_longer(names_to = "time_period", values_to = "live_weight", 
               cols = c(`Live weight 2010-2014`,`Live weight 2015-2019`)) %>%
  arrange(desc(live_weight)) %>%
    filter(exporter_iso3c == "NOR" |
          exporter_iso3c == "CHN" |
          exporter_iso3c == "ISL" |
          exporter_iso3c == "MAR" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "LVA" |
          exporter_iso3c == "VNM" |
          exporter_iso3c == "UKR" |
          exporter_iso3c == "CHL" |
          exporter_iso3c == "BLR" | 
          exporter_iso3c == "MRT" |
          exporter_iso3c == "DNK" |
          exporter_iso3c == "BLR" |
          exporter_iso3c == "IND" |
          exporter_iso3c == "GRL" |
          exporter_iso3c == "THA" ) %>%
  ggplot(aes(x= time_period, y = live_weight, color = exporter_iso3c, group = exporter_iso3c))+
  geom_line() +
  geom_point() +
 # scale_color_brewer(palette = "Paired")+
  xlab("")+
  ylab("Live Weight (Tons)")+ 
  ggtitle("Total Exports Before and After Annexation", subtitle = "Countries Exporting Seafood to Russia Faceted by Russian Embargo Counter-Sanction") +
 guides(col = guide_legend(title = "Russian Seafood Exporters"))+
   scale_y_continuous(breaks = seq(0, 2000000, by = 2000000))+
  scale_y_continuous(labels = scales::comma)+  
#  geom_segment(x = as.numeric(time_period), xend = as.numeric(time_period), y = 0, yend = 1000000)+
  facet_wrap(~exporter_sanctions_towards_russia.x)+
    theme(axis.text.x = element_text(angle = 10))

@@

Despite the initial dip in exports after the annexation, many countries' exports still increased overall between the two time periods. China and Morocco, in the countries who did not impose sanctions, saw their total exports fall, as did each country affected by the embargo, except for Denmark.
```{r}
top_exporters_all_years %>%
  replace(is.na(.), 0) %>%
  mutate(`Percent Change` = (`Live Weight 2015-2019 (Tons)` - `Live Weight 2010-2014 (Tons)`) / abs(`Live Weight 2015-2019 (Tons)`) * 100) %>%
      mutate(exporter_sanctions_towards_russia = case_when(
      Exporter %in% c("USA", "AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROM", "SVK", "SVN", "ESP", "SWE", "GBR", "JPN", "ALB", "ISL", "AUS", "MNT", "UKR", "CAN", "NOR", "CHE", "MDA")  ~ "yes",
      TRUE ~ "no"
    )) %>%
  ggplot() +
  geom_segment(mapping = aes( x = 0, xend = `Percent Change`, y = Exporter, yend = Exporter, color = exporter_sanctions_towards_russia)) +
  geom_point(mapping = aes(x= `Percent Change`, y = Exporter, color = exporter_sanctions_towards_russia))+
  xlab("Percent Change")+
  ylab("Exporters")+
  ggtitle("Percent Change in Exports to Russia After Crimean Annexation") +
  guides(col = guide_legend(title = "Sanctions Imposed by Russia"))+
      geom_vline(xintercept = 0)
```

@@

Trade trends with Russia can be seen when the imports and exports are broken down by the top species, rather than country. It is evident that Russia stopped importing as many seafood goods due to its agricultural embargo. Instead, Russia increased domestic supply to become more agriculturally self-reliant and food secure, and exported much more than it did prior to the Annexation. Its primary method was capture fisheries. Russia exported more seafood than it imported by an order of magnitude.

@@

ggplot(artis_russia_2009_2019 %>%
         filter(year %in% 2010:2019) %>%
  filter( importer_iso3c == "RUS") %>%
 filter(sci_name == "clupea harengus" | sci_name == "osteichthyes" | sci_name == "salmo salar" | sci_name == "animalia" | sci_name == "scomber scombrus" | sci_name == "sardina pilchardus" | sci_name == "sprattus sprattus" | sci_name == "mallotus villosus" | sci_name == "actinopteri" | sci_name == "oncorhynchus mykiss" | sci_name == "pangasianodon hypophthalmus"| sci_name == "mytilus chilensis"))+
    geom_col(aes(x= year, y= live_weight_t, fill = sci_name))+
              facet_wrap(~method)+
#  theme_solarized()+
  scale_color_solarized()+
  ggtitle("Top Russian Seafood Imports")+
  xlab("Year")+
  ylab("Live Weight (Tons)")+
  guides(fill = guide_legend(title = "Species"))+
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(breaks = seq(0,800000,by = 100000))+
  scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(n.breaks = 10)+
  geom_vline(xintercept = 2014)

@@

```{r include=FALSE}
# Animalia does not show up color-wise as great here because it spans multiple 4digit codes, whereas the ones above were grouped by sci name, not hs 4 digit code

@@

```{r, echo=FALSE, fig.height=6, fig.width=7}

@@

```{r, echo=FALSE, message= FALSE}

@@

```{r, echo = FALSE, message=FALSE, fig.height= 6, fig.cap = "Filtered by Change greater than 10,000 tons to show highest Exporting Countries to Russia"}
russian_import_change %>%
  rename(`Russian Import Trade Change` = russian_import_change_weight, `Russia-exempt Import Trade Change` = total_trade_change) %>%
  filter(exporter_iso3c != "RUS") %>%
  filter(abs(`Russian Import Trade Change`) > 10000 |
           abs(`Russia-exempt Import Trade Change`) > 10000) %>%
  select(exporter_iso3c, `Russian Import Trade Change`, `Russia-exempt Import Trade Change`, exporter_sanctions_towards_russia) %>%
  pivot_longer(`Russian Import Trade Change`:`Russia-exempt Import Trade Change`, names_to = "trade_type", values_to = "trade_change") %>%
  ggplot()+
  geom_segment(mapping = aes( x = 0, xend = trade_change, y = exporter_iso3c, yend = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
  geom_point(mapping = aes(x= trade_change, y = exporter_iso3c, color = trade_type, group = exporter_iso3c)) +
    geom_vline(xintercept = 0) +
    theme_bw()+
  xlab("Live Weight (Tons)")+
  ylab("Exporters to Russia")+
  ggtitle("Russian Imports Trade Change after Annexation", subtitle = "Faceted by Embargoed Nations")+
  scale_x_continuous(breaks= seq(-2500000, 3000000, by = 1000000))+
  scale_x_continuous(labels= scales::comma) +
  facet_wrap(~exporter_sanctions_towards_russia)+
      guides(col = guide_legend(title = "Trade Type"))

@@

There was little trade change in countries who did not face the embargo, but in countries that did, their total trade decreased, except for, again, Denmark. Russia did not import as many goods from China, even though it's exports to China increased. This was a common theme in Russian trade after the Annexation. In nations that faced the embargo, their total exports decreased as well, so Russia may have been a significant source of exports for them.

```{r}

@@

Countries that imposed sanctions on Russia, for the most part, still continued or increased their Russian seafood imports. The exceptions were Germany, and the USA. South Korea's imports also decreased, but it would go on to adopt Western sanctions against Russia in the Russian-Ukrainian War in 2022. Still, with variable degrees of import changes indeterminate of sanction status, there is no clear trend to predict import changes.

@@

The species did not change, either. The species trade was broken down to see if certain embargoed products were being reworked into a non-agricultural good, but the top HS codes did not change, and included HS 03, 05, 16, and 23, corresponding to fresh, chilled, or frozen fish and invertebrates; animal products; prepared seafood; and fish meal, respectively. No change in HS code trade shows that there was no tertiary market for alternate seafood goods.

This is shown, too, in total trade changes between Russia and the global seafood trade network. Most nations that enacted sanctions towards Russia saw an increase in imports directly from Russia and an increase in total imports originating in Russia. Their total exports, however, decreased, when they were banned from exporting to Russia. This may be a constraint of the dataset, however, as every piece of data was connected to Russia in some way. The opposite happened in Denmark, which experienced an increase in both Russia and total trade. Future work may include expanding trade view around Denmark to include nations using Danish waters and docking in Denmark, or if embargoed nations traded more with Denmark.

The total trade decreases and unchanging HS codes show that there likely was no teritary market that embargoed nations were using to get their seafood products to Russia. Overall, they were buying more goods, but selling less.

```{r}
# Example 3
# Showing all trade flows from producers to exporters to importers, 2010-2014

threshold <- 0.01

# Getting all producers limit by threshold
producers <- artis_russia_2009_2019 %>%
  filter(year %in% 2010:2014) %>%
  group_by(source_country_iso3c, exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(source_country_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ source_country_iso3c))

# Getting all exporters limit by threshold
exporters <- artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014) %>%
  group_by(exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(exporter_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ exporter_iso3c))

# Getting all importers limit by threshold
importers <- artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014) %>%
  group_by(importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(importer_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ importer_iso3c))

# Change all producers, exporters, and importers names based on limit threshold
artis_thresholded <- artis_russia_2009_2019 %>%
    filter(year %in% 2010:2014) %>%
  mutate(
    exporter_iso3c = case_when(
      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
      TRUE ~ "Other"
    ),
    importer_iso3c = case_when(
      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
      TRUE ~ "Other"
    ),
    source_country_iso3c = case_when(
      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
      TRUE ~ "Other"
    )
  ) %>%
  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t))

# Summarize trade flows from producers to exporters
source_exporter <- artis_thresholded %>%

  group_by(source_country_iso3c, exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
  rename(source = source_country_iso3c,
         target = exporter_iso3c)

# Summarize trade flows from exporters to importers
exporter_importer <- artis_thresholded %>%

  group_by(exporter_iso3c, importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
  rename(source = exporter_iso3c,
         target = importer_iso3c)

# Overall trade flow dataframes from producers -> exporters -> importers
tmp <- source_exporter %>%
  bind_rows(exporter_importer)

# Creating node dataframe from country names to node id
nodes <- data.frame(
  # Unique list of trading entity names
  name = unique(c(tmp$source, tmp$target))
  ) %>%
  # labels for sankey diagram only include country iso3 code
  mutate(label = gsub("_.{3,6}", "", name))

# Map source and target names to row in the nodes dataframe, 0-indexed
tmp <- tmp %>%
  mutate(source_id = match(source, nodes$name) - 1,
         target_id = match(target, nodes$name) - 1)

# Create Sankey Diagram
sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
              Value="live_weight_t", NodeID="label")

# Showing all trade flows from producers to exporters to importers, 2015-2019

threshold <- 0.01

# Getting all producers limit by threshold
producers <- artis_russia_2009_2019 %>%
  filter(year %in% 2015:2019) %>%
  group_by(source_country_iso3c, exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(source_country_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ source_country_iso3c))

# Getting all exporters limit by threshold
exporters <- artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019) %>%
  group_by(exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(exporter_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ exporter_iso3c))

# Getting all importers limit by threshold
importers <- artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019) %>%
  group_by(importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  ungroup() %>%
  mutate(total = sum(live_weight_t)) %>%
  mutate(prop = live_weight_t / total) %>%
  mutate(importer_iso3c = case_when(
    prop < threshold ~ "Other",
    TRUE ~ importer_iso3c))

# Change all producers, exporters, and importers names based on limit threshold
artis_thresholded <- artis_russia_2009_2019 %>%
    filter(year %in% 2015:2019) %>%
  mutate(
    exporter_iso3c = case_when(
      exporter_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ exporter_iso3c,
      TRUE ~ "Other"
    ),
    importer_iso3c = case_when(
      importer_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ importer_iso3c,
      TRUE ~ "Other"
    ),
    source_country_iso3c = case_when(
      source_country_iso3c %in% unique(c(producers$source_country_iso3c, exporters$exporter_iso3c, importers$importer_iso3c)) ~ source_country_iso3c,
      TRUE ~ "Other"
    )
  ) %>%
  group_by(source_country_iso3c, exporter_iso3c, importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t))

# Summarize trade flows from producers to exporters
source_exporter <- artis_thresholded %>%

  group_by(source_country_iso3c, exporter_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  mutate(source_country_iso3c = paste(source_country_iso3c, "_source", sep=""),
         exporter_iso3c = paste(exporter_iso3c, "_exp", sep="")) %>%
  rename(source = source_country_iso3c,
         target = exporter_iso3c)

# Summarize trade flows from exporters to importers
exporter_importer <- artis_thresholded %>%

  group_by(exporter_iso3c, importer_iso3c) %>%
  summarize(live_weight_t = sum(live_weight_t)) %>%
  mutate(exporter_iso3c = paste(exporter_iso3c, "_exp", sep=""),
         importer_iso3c = paste(importer_iso3c, "_imp", sep="")) %>%
  rename(source = exporter_iso3c,
         target = importer_iso3c)

# Overall trade flow dataframes from producers -> exporters -> importers
tmp <- source_exporter %>%
  bind_rows(exporter_importer)

# Creating node dataframe from country names to node id
nodes <- data.frame(
  # Unique list of trading entity names
  name = unique(c(tmp$source, tmp$target))
  ) %>%
  # labels for sankey diagram only include country iso3 code
  mutate(label = gsub("_.{3,6}", "", name))

# Map source and target names to row in the nodes dataframe, 0-indexed
tmp <- tmp %>%
  mutate(source_id = match(source, nodes$name) - 1,
         target_id = match(target, nodes$name) - 1)

# Create Sankey Diagram
sankeyNetwork(Links=tmp, Nodes = nodes, Source="source_id", Target="target_id",
              Value="live_weight_t", NodeID="label")

```{r}
###############
# Denmark 2010-2014
threshold <- 0.01
